Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-25 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Few changes

The three versions of the EvoDrawing web application were deployed to the
Heroku cloud service with the same configuration: using the
Heroku Free option with a 512 MB of RAM, adding only the GrapheneDB plug-in for the GG experiment.
Table \ref{tab:params} shows the parameters used for the evolutionary algorithm. The graph database 
system used in the implementation was Neo4J, and it was allready available as a plug-in in Heroku.

@@

% Anuncements
In order to start each of the experiments was promoted through social networks
particularly on the Facebook and Twitter platforms.
Is important to note that participants needed to log-in to facebook and give permissions to the application
in order to participate, there where no anonymous volunteers. This permited the automatic access to
each participant's social network permiting the construction a local network of friends participating.

The link used in the call for participation
was shortened URL, in order to obtain additional analytic data of the visitors.
In table \ref{tab:urls} the URL for each deployment in the Heroku platform is shown,
along with the short URL and the analytics link. In the same table a link to the GitHub 
application repository used to deploy to Heroku is also listed.

>>>>

The three versions of the EvoDrawing web application were deployed to the
Heroku cloud service with the same configuration: using the
Heroku Free option with a 512 MB of RAM, adding only the GrapheneDB and RedisTOGO plug-ins.
Table \ref{tab:params} shows the parameters used for the evolutionary algorithm. The graph database 
system used in the implementation was Neo4J as it was allready available as a plug-in in Heroku, is well documented
and a scalable solution \cite{miller2013graph,holzschuher2013performance}.

@@

% Anuncements
At the start of each of the experiments, a call to participation was promoted through social networks
particularly on Facebook and Twitter social networks.
Is important to note that participants needed to log-in to facebook and give permissions to the application
in order to participate, there were no anonymous volunteers. This permited the automatic access to
each participant's social network and to store a local copy of those friends also participating.

The link used in the call for participation
was shortened URL, in order to obtain additional data and analytic of the visitors.
In table \ref{tab:urls} the URL for each deployment in the Heroku platform is shown,
along with the short URL and the analytics link. In the same table a link to the GitHub 
application repository used to deploy to Heroku is also listed.
